Rmarkdown Features

### 2018-07-01 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up

@@

%設定行距
\linespread{1.2}\selectfont
```

>>>>

### PDF Output2
This is the yaml header for `bookdown::pdf_document2` output. Using `bookdown` extensions have several advantages. Search 'bookdown' for details.
```{yaml}
---
output:
  bookdown::pdf_document2:
    number_sections: FALSE
    toc: False
    includes:
      in_header: header.tex
    latex_engine: xelatex
  bookdown::html_document2:
    number_sections: FALSE
    includes:
      before_body: mathjax_bm.tex
urlcolor: blue
always_allow_html: yes
---
```

@@

%設定行距
\linespread{1.2}

%suppress page number
%\pagenumbering{gobble}
```
